Digital History in Finland, 1488-1828

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

field <- "subject_topic"
entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
s <- write_xtable(entries, file = paste(output.folder, catalog, "_Uppsala_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
```

>>>>

field <- "subject_topic"
entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
s <- write_xtable(entries, file = paste(output.folder, catalogue, "_Uppsala_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
```
